Horizontal and vertical diversity drive total biomass and its temporal stability in fish communities

### 2020-05-29 manuscript/bef_stability/manuscript.Rmd
Stuck to vertical diversity on total biomass

Biodiversity is a key to determine ecosystem properties
[@duffy_why_2009]. Current biodiversity losses and global changes question the
way in which ecosystems will be affected in turn [@bellard_impacts_2012]. Since
the seminal of paper of @may_will_1972, the relationships between
biodiversity and ecosystem properties have received a lot of attention [@hector_plant_1999;
@loreau_biodiversity_2001; @hooper_effects_2005; @dunne_network_2006;
@duffy_why_2009; @isbell_forest_quantifying_2018]. Because biodiversity largely
determines both the quantity and the distribution of matter and energy across
ecosystems, it has a tremendous effect on the properties exhibited by an
ecosystem, such as its total biomass [@hector_plant_1999;
@tilman_biodiversity_2014; @grace_integrative_2016;
@pennekamp_biodiversity_2018]], its biomass production
[@tilman_productivity_1996; @cardinale_species_2002; @grace_integrative_2016]
and the temporal stability of its biomass [@thebault_trophic_2005;
@thebault_relationship_2006; @tilman_biodiversity_2006;
@olivier_independent_nodate].

@@

Biodiversity can be quantified in numerous ways, as the number of species, i.e.
species richness and in number of functional groups, i.e. species are
gathered on what they do [@tilman_biodiversity_2014]. Those metrics can be
gathered into "horizontal diversity", describing the list of components present
in a community, i.e. here species and functional groups. An orthogonal
perspective, based on trophic chains, described species on what they eat. It can
be defined as interactions (or biomass/energy fluxes) between species and how
they are distributed among communities. It can be quantified as the number of
interaction between species or the number of trophic level. This orthogonal view
of seeing biodiversity, can be gathered into "vertical diversity". Horizontal
and vertical diversity are, however, not independent from each other
[@duffy_functional_2007; @zhao_horizontal_2019]. The add or removal of one
species can have different effects depending on its vertical position in the
trophic chain [@duffy_functional_2007]. Hence, it is crucial to study their
interplay to improve our understanding of ecosystem dynamics. 
(*This paragraph is surely too simplistic*)

@@

Horizontal and vertical diversity has been shown to promote higher biomass
production in a variety of ecosystems. Horizontal diversity, as species
richness, has been reported to increase productivity through complementarity
between species in resource exploitation and selection effects in plant
communities [@tilman_productivity_1996; @cardinale_species_2002;
@grace_integrative_2016].  Regarding total biomass, empirical assessment have
shown generally positive relationships with species richness in plant
communities [@hector_plant_1999; @tilman_biodiversity_2014, but see
@grace_integrative_2016], as in mesocosms [@pennekamp_biodiversity_2018].
Theoretical models have also confirmed that an increase in horizontal diversity
should translate into increase in plant biomass through resource complementarity
[@loreau_biodiversity_1998] and selection effects [@tilman_plant_1997]. The
addition of trophic levels, notably consumer on plants generally breaks the
positive relationship between plant biomass and plant diversity as a significant
amount of biomass is transfered to consumers [@thebault_food-web_2003]. It has
been shown both in experiments [REF] and theoretical models
[@thebault_food-web_2003].  @thebault_relationship_2006 have shown with a
theoretical model that total biomass should increase with the increase species
diversity at two trophic level. However, the joint effects of horizontal and
vertical diversity on total biomass has been rarely tested, especially in
natural communities. It is not clear whether horizontal and vertical diversity
just change the distribution of biomass across trophic level or it increases the
total amount of  biomass (*It misses a lot of references here*).

>>>>

Current biodiversity losses and global changes affect ecosystems in complex and
unpredictable ways [@bellard_impacts_2012]. Since the seminal of paper of
@may_will_1972, the relationships between biodiversity and ecosystem properties
have received a lot of attention [@hector_plant_1999; @loreau_biodiversity_2001;
@hooper_effects_2005; @dunne_network_2006; @duffy_why_2009;
@isbell_forest_quantifying_2018]. Biodiversity largely determines both the
amount and the distribution of matter and energy fluxes within ecosystems, and
has hence a tremendous effect on ecosystem properties [@duffy_why_2009], such as
its total biomass [@hector_plant_1999; @tilman_biodiversity_2014;
@grace_integrative_2016; @pennekamp_biodiversity_2018]], biomass production
[@tilman_productivity_1996; @cardinale_species_2002; @grace_integrative_2016]
and the biomass temporal stability [@thebault_trophic_2005;
@thebault_relationship_2006; @tilman_biodiversity_2006;
@olivier_independent_nodate].

@@

Biodiversity can be quantified in numerous ways: either as the number of species
(i.e.  species richness) and in number of functional groups, which are usually
defined based on the trophic ecology of species, namely the way they acquire
food [@allan_stream_2007]. Those metrics can be organized into (i) "horizontal
diversity", which captures the overall diversity of components (i.e. species)
present in a community, and (ii) "vertical diversity" which captures diversity
of components across functional groups, such as the amount trophic categories,
often termed guilds or levels [@allan_stream_2007; @loreau_population_2010;
@zhao_horizontal_2019; @wang_biodiversity_2017]. Vertical diversity has been
primarily quantified as food chain length [@loreau_population_2010;
@zhao_horizontal_2019; @wang_biodiversity_2017] but it can also be characterized
by the food web structure [@wang_biodiversity_2017] such as connectance and
average trophic level. Horizontal and vertical diversity are, however, not
independent from each other. Connectance is known to covary negatively with
species richness [@winemiller_must_1989; @dunne_network_2006;
@thebault_stability_2010].

**Horizontal and vertical diversity are, however, not independent from each other
[@duffy_functional_2007; @zhao_horizontal_2019]. The add or removal of one
species (i.e. ) can have different effects depending on its vertical position in the
trophic chain [@duffy_functional_2007]. Hence, it is crucial to study their
interplay to improve our understanding of ecosystem dynamics.**

@@

Horizontal diversity has been shown to promote higher biomass production in a
variety of ecosystems. Horizontal diversity, as species richness, has been
reported to increase primary productivity [@cardinale_species_2002,
@tilman_productivity_1996; @grace_integrative_2016]. Two mechanisms have been
proposed to rise this effect [@loreau_partitioning_2001]. The complementarity in
resource use, rising through niche differentiation and interspecific
facilitation, increase the total amount of resource used
[@loreau_biodiversity_1998; @cardinale_species_2002; @loreau_partitioning_2001].
Positive select effect arise when species richness leads to an higher dominance
of the most productive species [@tilman_plant_1997; @loreau_partitioning_2001].
As for total biomass, empirical studies have generally demonstrated positive
relationships with species richness in plant communities [@hector_plant_1999;
@tilman_biodiversity_2014; but see @grace_integrative_2016] and mesocosms
[@pennekamp_biodiversity_2018]. When adding the vertical diversity, e.g.
consumers species, @gamfelt_species_2005 and @thebault_relationship_2006 have found that total
biomass increased with increasing species diversity at two trophic levels.
But this positive relation seems to strongly depend on the niche differentiation of
the consumer species, i.e. their resource complementarity,
@thebault_relationship_2006. Hence, the total biomass-species richness
relationship seems to be supported by the same mechanisms within consumers and
within plants. (also duffy_ecosystem_2005)

The effect of the vertical diversity itself does not seem to affect total
biomass. But seek food chain length, connectance

You should connect average trophic level to biomass repartition (good when lots
of omnivory and no trophic chain)

- Effect of food web structure on total biomass are relatively absent

However, increasing consumer species richness
results in higher consumer biomass to the detriment of primary producer biomass
[@gamfelt_species_2005; @thebault_relationship_2006].

- Horizontal div at different trophic levels (v & h )
- Vertical div:

The food web structure, vertical diversity, also modulates total biomass and
productivity [@thebault_food-web_2003; @thebault_trophic_2005;
@ogorman_multiple_2012; @dossena_warming_2012; @schneider_animal_2016;
@gamfelt_species_2005]. Both in theoretical and experimental study,

The addition of trophic levels, consumer usually
breaks the positive relationship between plant biomass and plant diversity as a
significant amount of biomass is transfered to consumers
[@thebault_food-web_2003].

It has been shown both in experiments
[@ogorman_multiple_2012; @dossena_warming_2012]
and theoretical models [@thebault_food-web_2003; @schneider_animal_2016;
@wang_biodiversity_2017].

Theoretical models @thebault_relationship_2006
have shown with a theoretical model that total biomass should increase with the
increase species diversity at two trophic level *+[]*. However, the joint effects of horizontal and vertical
diversity on total biomass has been rarely tested, especially in natural
communities. It is not clear whether horizontal and vertical diversity just
change the distribution of biomass across trophic level or it increases the
total amount of  biomass (*It misses a lot of references here*).
